GVN-Hoist: Hoisting Computations from Branches

### 2016-08-04 hoist.tex
rewrite abstract

\title{GVN-hoist: hoisting expressions from control flow}

@@

\maketitle
\begin{abstract}
  Code hoisting identifies identical computations and replaces them with a
  single expression in the common dominator.  Code hoisting is often confused
  with CSE (Common Subexpression Elimination) although is not bound to find
  redundancies within a single basic block.  It could also be confused with PRE,
  although the main goal is not to remove redundancies: it enables removal of
  redundancies by other passes like LICM.  The main goal of code hoisting is to
  reduce code size with added benefit of exposing instruction level parallelism
  and reduced register pressure.
\end{abstract}

@@

\subsection{Enabling LICM by code-hoisting}
loop:
if (a)
  i1;
else
  i1;

@@

e.g.
BB1
load a;
....
store .;
....
load a;

@@

BB0 -> BB1
BB0 -> BB2

>>>>

\title{GVN-Hoist: Hoisting Computations from Branches}

@@

\maketitle
\begin{abstract}
  Code hoisting identifies identical computations across the program with the
  help of a Global Value Numbering (GVN) analysis, identifies a hoisting
  position that dominates all the identical computations and in which all
  operands are avaialable, duplicates one of the expressions in the hoisting
  position, and removes all the computations now redundant in their original
  position.

  Code hoisting is often confused with CSE (Common Subexpression Elimination)
  although hoisting is not bound to find redundancies within a single basic
  block.  Code hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or even with Global Common Subexpression Elimination (GCSE)
  although the main goal of code hoisting is not to remove redundancies: code
  hoisting effectively exposes redundancies and enables other passes like LICM
  to remove more redundancies.  The main goal of code hoisting is to reduce code
  size with the added benefit of exposing instruction level parallelism and
  reduced register pressure.
\end{abstract}

@@

\subsection{Enabling LICM by code-hoisting}

\begin{verbatim}
loop:
if (a)
  i1;
else
  i1;
\end{verbatim}

@@

e.g.
\begin{verbatim}
BB1
load a;
....
store .;
....
load a;

@@

BB0 -> BB1
BB0 -> BB2
\end{verbatim}
